Extended Data

### 2022-03-07 doc/manuscript/Dow_manuscript_Nature.Rmd
Update Dow_manuscript_Nature.Rmd

- stem growth is routinely used to estimate woody productivity (but wood density partially decouples them) [@delpierre_wood_2016 and refs therein]
- stem growth and woody productivity are decoupled from GPP[@delpierre_wood_2016 and refs therein]
- close coordination of budburst and initiation of xylogenesis[@delpierre_temperate_2016]
- start of xylogenesis makes growth possible, but actual growth depends on climate conditions during the growth period
- probably include some mention of conifers (for whcih more work has been done)

@@

As climate change accelerates and spring temperatures become increasingly warmer, growing seasons will start earlier; however, barring rapid acclimation of forests to the warming conditions, advancement in the timing of stem growth (Fig. 1) is unlikely to provide the sustained increase in CO~2~ sequestration in woody biomass and ensuant negative climate change feedback that is anticipated in most climate forecasting models[@buermann_widespread_2018;@zani_increased_2020;@keenan_net_2014;@ahlstrom_robustness_2012].
Rather, the dominant effect of rising temperatures on forest woody productivity will be a negative effect of high summer temperatures (Fig. 3), which constitutes a positive feedback to climate change.

>>>>

- stem growth is routinely used to estimate woody productivity (but wood density partially decouples them) [@delpierre_wood_2016 and refs therein]
- stem growth and woody productivity are decoupled from GPP[@delpierre_wood_2016 and refs therein]
- close coordination of budburst and initiation of xylogenesis[@delpierre_temperate_2016]
- start of xylogenesis makes growth possible, but actual growth depends on climate conditions during the growth period
- probably include some mention of conifers (for whcih more work has been done)
- cite @gao_earlier_2022, noting that their result may be driven by conifers

@@

As climate change accelerates and spring temperatures become increasingly warmer, growing seasons will start earlier; however, barring rapid acclimation of temperate deciduous forests to the warming conditions, advancement in the timing of stem growth (Fig. 1) is unlikely to provide the sustained increase in CO~2~ sequestration in woody biomass and ensuant negative climate change feedback that is anticipated in most climate forecasting models[@buermann_widespread_2018;@zani_increased_2020;@keenan_net_2014;@ahlstrom_robustness_2012].
<!--gao_earlier_2022 demonstrates the same for some other regions.-->
Rather, the dominant effect of rising temperatures on forest woody productivity will be a negative effect of high summer temperatures (Fig. 3), which constitutes a positive feedback to climate change.
